---
title: "ERQ1"
output: 
  html_document: 
    toc: yes
    keep_md: yes
date: '2022-05-02'
---


```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Preregistration available From: https://osf.io/er4v5?view_only=edf4718aa62947dc9277c4a4749e4628


Exploratory research questions

ERQ1. If childlessness is associated with the economic left-right position of the party for which one has voted, are those associations stronger if this dimension is salient in the party’s public stance (i.e., is there a boundary condition to these associations, such that the ideology needs to be salient in order for the association to exist)?


# Preparations

## Packages

```{r}

library(lme4)
library(emmeans)
library(rio)
library(dplyr)
library(vjihelpers)
library(ggplot2)
library(MetBrewer)
library(tibble)
library(Hmisc)

```

## Custom functions

```{r}
source("../custom_functions.R")

```

## Data

```{r}
fdat<-import("../../data/processed/fdat.xlsx")
```

## Data exclusions

```{r}

exdat<-fdat %>%
  dplyr::select(childlessness,
                gndr.f,agea,minority,
                gndr.c,age10.c,minority.c,
                lrecon.z,
                lrecon_salience.z,
                cntry,
                anweight) %>%
  na.omit()
```

## Variable centering

```{r}
exdat<-
  group_mean_center(
    data=exdat,group.var="cntry",
    vars=c("lrecon.z",
           "lrecon_salience.z"),
    grand.init = F)

```

# ERQ1 Analysis 

### Fixed

```{r}
mod2.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),
        weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod2.lrecon)
getFE_glmer(mod2.lrecon)
getVC(mod2.lrecon)

```

### Random

```{r}
mod3.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+
          (lrecon.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.lrecon)
getFE_glmer(mod3.lrecon)
getVC(mod3.lrecon)

```


### Random without random effect correlation

```{r}
mod4.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+
          (lrecon.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod4.lrecon)

getFE_glmer(mod4.lrecon)
getVC(mod4.lrecon)

anova(mod2.lrecon,mod4.lrecon)
anova(mod4.lrecon,mod3.lrecon)


```






## lrecon salience fixed main effect

```{r}
mod5.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+lrecon_salience.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod5.lrecon)
getFE_glmer(mod5.lrecon)
getVC(mod5.lrecon)

```

## lrecon salience random main effect

```{r}
mod6.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+lrecon_salience.z.gmc+
          (lrecon_salience.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod6.lrecon)
getFE_glmer(mod6.lrecon)
getVC(mod6.lrecon)
```



## fixed interaction between lrecon and lrecon salience

```{r}
mod8.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+lrecon_salience.z.gmc+
          lrecon.z.gmc:lrecon_salience.z.gmc+
          (lrecon_salience.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod8.lrecon)
getFE_glmer(mod8.lrecon)
getVC(mod8.lrecon)


```


## fixed interaction between lrecon and lrecon salience without random effect correlation

```{r}
mod9.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+lrecon_salience.z.gmc+
          lrecon.z.gmc:lrecon_salience.z.gmc+
          (lrecon_salience.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod9.lrecon)
getFE_glmer(mod9.lrecon)
getVC(mod9.lrecon)


```

## random interaction between lrecon and lrecon salience without random effect correlations

```{r}
mod10.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+lrecon_salience.z.gmc+
          lrecon.z.gmc:lrecon_salience.z.gmc+
          (lrecon.z.gmc:lrecon_salience.z.gmc+
             lrecon_salience.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod10.lrecon)
getFE_glmer(mod10.lrecon)
getVC(mod10.lrecon)

anova(mod9.lrecon,mod10.lrecon)


```

### marginal effects

```{r}
emtrends(mod9.lrecon,
         var="lrecon.z.gmc",
         specs="lrecon_salience.z.gmc",
         at=list(lrecon_salience.z.gmc=c(-1,0,1)),
         infer=c(T,T))

emtrends(mod9.lrecon,
         var="lrecon.z.gmc",
         specs="lrecon_salience.z.gmc",
         at=list(lrecon_salience.z.gmc=c(-1,0,1)),
         infer=c(T,T),regrid="response")


```





### Plot

```{r}
range(exdat$lrecon_salience.z.gmc)
hist(exdat$lrecon_salience.z.gmc)
quantile(exdat$lrecon_salience.z.gmc,c(.25,.50,.75))

p<-
  emmip(mod9.lrecon, lrecon_salience.z.gmc ~ lrecon.z.gmc,
        at=list(lrecon_salience.z.gmc = c(-1,0,1),
                #minority.c = c(-0.5,0.5),
                lrecon.z.gmc=seq(from=-3.05,to=1.15,by=0.01)),
        plotit=F,CIs=TRUE,type="response")

head(p)

#p$ethnic_minority=
#  ifelse(p$minority.c==(-0.5),
#         "Ethnic majority","Ethnic minority")
p$lrecon_salience<-p$tvar
levels(p$lrecon_salience)<-
  c("Low Salience","Average Salience","High Salience")


min.low<-
  min(exdat[exdat$lrecon_salience.z.gmc<=(-1),
            "lrecon.z.gmc"])
max.low<-
  max(exdat[exdat$lrecon_salience.z.gmc<=(-1),
            "lrecon.z.gmc"])


p$filter.low<-
  ifelse(p$lrecon_salience.z.gmc==(-1) &
           (p$lrecon.z.gmc<min.low | 
              p$lrecon.z.gmc>max.low),0,1)

table(p$filter.low)

min.mid<-
  min(exdat[exdat$lrecon_salience.z.gmc>(-1) |
              exdat$lrecon_salience.z.gmc<(1),
            "lrecon.z.gmc"])
max.mid<-
  max(exdat[exdat$lrecon_salience.z.gmc>(-1) |
              exdat$lrecon_salience.z.gmc<(1),
            "lrecon.z.gmc"])


p$filter.mid<-
  ifelse(p$lrecon_salience.z.gmc==(0) &
           (p$lrecon.z.gmc<min.mid | 
              p$lrecon.z.gmc>max.mid),0,1)

table(p$filter.mid)

min.high<-
  min(exdat[exdat$lrecon_salience.z.gmc>=(1) ,
            "lrecon.z.gmc"])
max.high<-
  max(exdat[exdat$lrecon_salience.z.gmc>=(1) ,
            "lrecon.z.gmc"])

p$filter.high<-
  ifelse(p$lrecon_salience.z.gmc==(1) &
           (p$lrecon.z.gmc<min.high | 
              p$lrecon.z.gmc>max.high),0,1)

table(p$filter.high)

p.ex<-p[p$filter.low!=0 & p$filter.mid!=0 & p$filter.high!=0,]

met.brewer("Archambault")
met.brewer("Archambault")[c(1,3,2)]

p1<-ggplot(p.ex,aes(y=yvar,x=xvar,color=lrecon_salience))+
  geom_point(size=3)+
  geom_errorbar(aes(ymin=LCL, ymax=UCL),alpha=0.5)+
  xlab("Economic Left-Right")+
  ylab("P(Childlessness)")+
  scale_color_manual(values=met.brewer("Archambault")[c(1,3,2)])+
  facet_wrap(~lrecon_salience,ncol=3)+
  theme(legend.position = "none",
        text=element_text(size=16,  family="sans"),
        panel.background = element_rect(fill = "white",
                                        #colour = "black",
                                        #size = 0.5, linetype = "solid"
                                        ),
        panel.grid.major.x = element_line(size = 0.5, linetype = 2,
                                        colour = "black"))
p1

png(filename = 
      "../../results/figures/lrecon_lrecon_salience_nonextrp.png",
    units = "cm",
    width = 29.7,height=21.0,res = 600)
p1
dev.off()

```


```{r}
sinf<-sessionInfo()
print(sinf,locale=F)
```
