---
title: "ERQ5. West vs. post-communist moderation"
output: 
  html_document: 
    toc: yes
    keep_md: yes
date: '2022-05-02'
---


```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

ERQ5. Are the associations between childlessness and the ideology positions, salience of anti-elitism and (anti-)corruption, and policy positions of the party for which one has voted different in Western Europe and in post-communist countries?

Random slopes were detected for international_security and antielite_salience.


# Preparations

## Packages

```{r}
library(lme4)
library(emmeans)
library(rio)
library(dplyr)
library(vjihelpers)
library(ggplot2)

```

## Custom functions

```{r}
source("../custom_functions.R")
```

## Data

```{r}
fdat<-import("../../data/processed/fdat.xlsx")
```

## Code West and post-communist countries

```{r}
table(fdat$cntry)

fdat$West_vs_post_comm<-
  case_when(fdat$cntry == "AT" |
              fdat$cntry == "BE" |
              fdat$cntry == "CH" |
              fdat$cntry == "DE" |
              fdat$cntry == "DK" |
              fdat$cntry == "ES" |
              fdat$cntry == "FI" |
              fdat$cntry == "FR" |
              fdat$cntry == "GB" |
              fdat$cntry == "IE" |
              fdat$cntry == "IL" |
              fdat$cntry == "NL" |
              fdat$cntry == "NO" |
              fdat$cntry == "PT" |
              fdat$cntry == "SE" ~ -0.5,
            TRUE~0.5)

table(fdat$West_vs_post_comm,useNA="always")
```

## Random effect tests

This script prints the random effect models that were significant

```{r}
varnames<-
  names(fdat)[which(names(fdat)=="lrgen"):
              which(names(fdat)=="corrupt_salience")]


for (i in 1:length(varnames)){
  MC1<-import(paste0(getwd(),"/",varnames[i],"/mod3_MC.xlsx"))
  MC2<-import(paste0(getwd(),"/",varnames[i],"/mod4_MC.xlsx"))
  if (MC1[2,"Pr..Chisq."]<.05 |
      MC2[2,"Pr..Chisq."]<.05) {
    print(varnames[i])
  }

}

```

## Data exclusions

```{r}

exdat<-fdat %>%
  dplyr::select(childlessness,
                gndr.c,age10.c,
                minority.c,
                West_vs_post_comm,
                deregulation.z,
                redistribution.z,
                international_security.z,
                antielite_salience.z,
                cntry,anweight) %>%
  na.omit()

```

## Variable centering

```{r}
exdat<-
  group_mean_center(
    data=exdat,group.var="cntry",
    vars=c("deregulation.z",
          "redistribution.z",
           "international_security.z",
           "antielite_salience.z"),
    grand.init = F)

```


# Analysis 

## deregulation

### Fixed main effect

```{r}
mod2.deregulation<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          deregulation.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.deregulation)
```

### Random main effect

```{r}
mod3.deregulation<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          deregulation.z.gmc+
          (deregulation.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.deregulation)

anova(mod2.deregulation,mod3.deregulation)
```

### West vs. post-communist main effect

```{r}
mod4.deregulation<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          West_vs_post_comm+
          deregulation.z.gmc+
          (deregulation.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod4.deregulation)

anova(mod3.deregulation,mod4.deregulation)
```

### West vs. post-communist x deregulation interaction

```{r}
mod5.deregulation<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          West_vs_post_comm+
          deregulation.z.gmc+
          West_vs_post_comm:deregulation.z.gmc+
          (deregulation.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod5.deregulation)
getFE_glmer(mod5.deregulation)
getVC(mod5.deregulation)

anova(mod4.deregulation,mod5.deregulation)
```

#### Marginal effects

```{r}
emtrends(mod5.deregulation,
         var="deregulation.z.gmc",
         specs="West_vs_post_comm",
         at=list(West_vs_post_comm=c(-0.5,0.5)),infer=c(T,T))

emtrends(mod5.deregulation,
         var="deregulation.z.gmc",
         specs="West_vs_post_comm",
         at=list(West_vs_post_comm=c(-0.5,0.5)),infer=c(T,T),
         regrid="response")
```


## redistribution

### Fixed main effect

```{r}
mod2.redistribution<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          redistribution.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.redistribution)
```

### Random main effect

```{r}
mod3.redistribution<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          redistribution.z.gmc+
          (redistribution.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.redistribution)

anova(mod2.redistribution,mod3.redistribution)
```

### Random main effect without correlation

```{r}
mod3.redistribution<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          redistribution.z.gmc+
          (redistribution.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.redistribution)

anova(mod2.redistribution,mod3.redistribution)
```

### West vs. post-communist main effect

```{r}
mod4.redistribution<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          West_vs_post_comm+
          redistribution.z.gmc+
          (redistribution.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod4.redistribution)

anova(mod3.redistribution,mod4.redistribution)
```

### West vs. post-communist x redistribution interaction

```{r}
mod5.redistribution<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          West_vs_post_comm+
          redistribution.z.gmc+
          West_vs_post_comm:redistribution.z.gmc+
          (redistribution.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod5.redistribution)
getFE_glmer(mod5.redistribution)
getVC(mod5.redistribution)

anova(mod4.redistribution,mod5.redistribution)
```

#### Marginal effects

```{r}
emtrends(mod5.redistribution,
         var="redistribution.z.gmc",
         specs="West_vs_post_comm",
         at=list(West_vs_post_comm=c(-0.5,0.5)),infer=c(T,T))

emtrends(mod5.redistribution,
         var="redistribution.z.gmc",
         specs="West_vs_post_comm",
         at=list(West_vs_post_comm=c(-0.5,0.5)),infer=c(T,T),
         regrid="response")
```



## international_security

### Fixed main effect

```{r}
mod2.international_security<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          international_security.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod2.international_security)
```

### Random main effect

```{r}
mod3.international_security<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          international_security.z.gmc+
          (international_security.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.international_security)

anova(mod2.international_security,mod3.international_security)
```

### Random main effect without correlation

```{r}
mod3.international_security<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          international_security.z.gmc+
          (international_security.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.international_security)

anova(mod2.international_security,mod3.international_security)
```

### West vs. post-communist main effect

```{r}
mod4.international_security<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          West_vs_post_comm+
          international_security.z.gmc+
          (international_security.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod4.international_security)

anova(mod3.international_security,mod4.international_security)
```

### West vs. post-communist x international_security interaction

```{r}
mod5.international_security<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          West_vs_post_comm+
          international_security.z.gmc+
          West_vs_post_comm:international_security.z.gmc+
          (international_security.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod5.international_security)
getFE_glmer(mod5.international_security)
getVC(mod5.international_security)

anova(mod4.international_security,mod5.international_security)
```

#### Marginal effects

```{r}
emtrends(mod5.international_security,
         var="international_security.z.gmc",
         specs="West_vs_post_comm",
         at=list(West_vs_post_comm=c(-0.5,0.5)),infer=c(T,T))

emtrends(mod5.international_security,
         var="international_security.z.gmc",
         specs="West_vs_post_comm",
         at=list(West_vs_post_comm=c(-0.5,0.5)),infer=c(T,T),
         regrid="response")
```

## antielite_salience

### Fixed main effect

```{r}
mod2.antielite_salience<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          antielite_salience.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod2.antielite_salience)
```

### Random main effect

```{r}
mod3.antielite_salience<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          antielite_salience.z.gmc+
          (antielite_salience.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.antielite_salience)

anova(mod2.antielite_salience,mod3.antielite_salience)
```

### Random main effect

```{r}
mod3.antielite_salience<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          antielite_salience.z.gmc+
          (antielite_salience.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod3.antielite_salience)

anova(mod2.antielite_salience,mod3.antielite_salience)
```

### West vs. post-communist main effect

```{r}
mod4.antielite_salience<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          West_vs_post_comm+
          antielite_salience.z.gmc+
          (antielite_salience.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod4.antielite_salience)

anova(mod3.antielite_salience,mod4.antielite_salience)
```

### West vs. post-communist x antielite_salience interaction

```{r}
mod5.antielite_salience<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          West_vs_post_comm+
          antielite_salience.z.gmc+
          West_vs_post_comm:antielite_salience.z.gmc+
          (antielite_salience.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod5.antielite_salience)
getFE_glmer(mod5.antielite_salience)
getVC(mod5.antielite_salience)

anova(mod4.antielite_salience,mod5.antielite_salience)
```

#### Marginal effects

```{r}
emtrends(mod5.antielite_salience,
         var="antielite_salience.z.gmc",
         specs="West_vs_post_comm",
         at=list(West_vs_post_comm=c(-0.5,0.5)),infer=c(T,T))

emtrends(mod5.antielite_salience,
         var="antielite_salience.z.gmc",
         specs="West_vs_post_comm",
         at=list(West_vs_post_comm=c(-0.5,0.5)),infer=c(T,T),
         regrid="response")
```



```{r}
sinf<-sessionInfo()
print(sinf,locale=F)
```
