---
title: "RQ1, RQ2, ERQ1, ERQ2"
output: 
  html_document: 
    toc: yes
    keep_md: yes
date: '2022-05-02'
---


```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

RQ1. Is childlessness associated with the three Chapel Hill rated political ideology (Left-Right, Economic Left-Right, GAL-TAN) positions of the party for which one has voted? 

H1. Regarding GAL-TAN, we expect childless people to have voted closer to the GAL pole of the dimension.

RQ2. If, as expected (H1), childlessness is associated with the GAL-TAN ideology position of the party for which one has voted, are those associations stronger if this dimension is salient in the party’s public stance (i.e., is there a boundary condition to these associations, such that the ideology needs to be salient in order for the association to exist)?

H2. We expect the association between childlessness and the GAL-TAN political ideology of the party for which one has voted to be stronger if this dimension is salient in the party’s public stance.

Exploratory research questions

ERQ1. If childlessness is associated with the economic left-right position of the party for which one has voted, are those associations stronger if this dimension is salient in the party’s public stance (i.e., is there a boundary condition to these associations, such that the ideology needs to be salient in order for the association to exist)?

ERQ2. Is childlessness associated with any of the 15 Chapel Hill rated policy positions of the party for which one has voted, or with the salience of anti-elitism or anti-corruption in the party agenda?


# Preparations

## Packages

```{r}
library(lme4)
library(emmeans)
library(rio)
library(dplyr)
library(vjihelpers)
library(ggplot2)

```

## Custom functions

```{r}
source("../custom_functions.R")
source("../modglmer_logit.R")
```

## Data

```{r}
fdat<-import("../../data/processed/fdat.xlsx")
```

## Data exclusions

```{r}
names(fdat)

exdat<-fdat %>%
  dplyr::select(childlessness,
                gndr.c,age10.c,minority.c,
                lrgen,
                lrecon,galtan,
                lrecon_salience,galtan_salience,
                cntry,anweight) %>%
  na.omit()
```

## Variable centering

```{r}
exdat<-
  group_mean_center(
    data=exdat,group.var="cntry",
    vars=c("lrgen","lrecon","galtan",
           "lrecon_salience","galtan_salience"),
    grand.init = F)

```

## Variable scaling

```{r}
CHES<-
  import("../../data/raw/2014_CHES_dataset_means.csv")

(sd.lrgen<-sd(CHES$lrgen,na.rm=T))
(sd.lrecon<-sd(CHES$lrecon,na.rm=T))
(sd.galtan<-sd(CHES$galtan,na.rm=T))
(sd.galtan_salience<-sd(CHES$galtan_salience,na.rm=T))
(sd.lrecon_salience<-sd(CHES$lrecon_salience,na.rm=T))

exdat$lrgen.z.gmc<-exdat$lrgen.gmc/sd.lrgen
exdat$lrecon.z.gmc<-exdat$lrecon.gmc/sd.lrecon
exdat$galtan.z.gmc<-exdat$galtan.gmc/sd.galtan
exdat$galtan_salience.z.gmc<-
  exdat$galtan_salience.gmc/sd.galtan_salience
exdat$lrecon_salience.z.gmc<-
  exdat$lrecon_salience.gmc/sd.lrecon_salience
```

# Descriptives

```{r}
table(exdat$cntry,exdat$childlessness)
round(100*prop.table(table(exdat$cntry,
                           exdat$childlessness),1),1)

prop.table(table(exdat$childlessness))
```

# RQ1 Analysis 


RQ1. Is childlessness associated with the three Chapel Hill rated political ideology (Left-Right, Economic Left-Right, GAL-TAN) positions of the party for which one has voted? 

H1. Regarding GAL-TAN, we expect childless people to have voted closer to the GAL pole of the dimension.

## Baserate only


```{r}
mod0<-
  glmer(childlessness~(1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)

summary(mod0)
```

## Covariates

```{r}
mod1<-
  glmer(childlessness~gndr.c+age10.c+minority.c+(1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)

summary(mod1)
```

## lrgen

### Fixed

```{r}
mod2.lrgen<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrgen.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.lrgen)
```

### Random

```{r}
mod3.lrgen<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrgen.z.gmc+
          (lrgen.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.lrgen)

anova(mod2.lrgen,mod3.lrgen)
```


## lrecon

### Fixed

```{r}
mod2.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.lrecon)
```

### Random

```{r}
mod3.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+
          (lrecon.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.lrecon)

anova(mod2.lrecon,mod3.lrecon)
```



## galtan

### Fixed

```{r}
mod2.galtan<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          galtan.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.galtan)
```

### Random

```{r}
mod3.galtan<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          galtan.z.gmc+
          (galtan.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.galtan)

anova(mod2.galtan,mod3.galtan)
```

# RQ2 Analysis 

RQ2. If, as expected (H1), childlessness is associated with the GAL-TAN ideology position of the party for which one has voted, are those associations stronger if this dimension is salient in the party’s public stance (i.e., is there a boundary condition to these associations, such that the ideology needs to be salient in order for the association to exist)?

H2. We expect the association between childlessness and the GAL-TAN political ideology of the party for which one has voted to be stronger if this dimension is salient in the party’s public stance.

## galtan salience fixed main effect

```{r}
mod4.galtan<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          galtan.z.gmc+galtan_salience.z.gmc+
          (galtan.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod4.galtan)
```

## fixed interaction between galtan and galtan salience

```{r}
mod5.galtan<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          galtan.z.gmc+galtan_salience.z.gmc+
          galtan.z.gmc:galtan_salience.z.gmc+
          (galtan.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod5.galtan)
```

### marginal effects

```{r}
emtrends(mod5.galtan,
         var="galtan.z.gmc",
         specs="galtan_salience.z.gmc",
         at=list(galtan_salience.z.gmc=c(-1,0,1)),
         infer=c(T,T))

```



## random interaction between galtan and galtan salience

```{r}
mod6.galtan<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          galtan.z.gmc+galtan_salience.z.gmc+
          galtan.z.gmc:galtan_salience.z.gmc+
          (galtan.z.gmc+galtan_salience.z.gmc+
             galtan.z.gmc:galtan_salience.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod6.galtan)
```


### Plot

```{r}

p<-
  emmip(mod5.galtan, galtan_salience.z.gmc ~ galtan.z.gmc,
        at=list(galtan_salience.z.gmc = c(-1,0,1),
                #minority.c = c(-0.5,0.5),
                galtan.z.gmc=seq(from=-2,to=2,by=0.02)),
        plotit=F,CIs=TRUE,type="response")

head(p)

#p$ethnic_minority=
#  ifelse(p$minority.c==(-0.5),
#         "Ethnic majority","Ethnic minority")
p$galtan_salience<-p$tvar
levels(p$galtan_salience)



p2<-ggplot(p,aes(y=yvar,x=xvar,color=galtan_salience))+
  geom_point()+
  geom_errorbar(aes(ymin=LCL, ymax=UCL),alpha=0.5)+
  xlab("Left-Right Economic")+
  ylab("P(Childlessness)")
p2

png(filename = 
      "../../results/figures/galtan_galtan_salience.png",
    units = "cm",
    width = 20.0,height=10.0,res = 300)
p2
dev.off()
```

### Non-extrapolated plot

```{r}

min.low<-
  min(exdat[exdat$galtan_salience.z.gmc<=(-1),
            "galtan.z.gmc"])
max.low<-
  max(exdat[exdat$galtan_salience.z.gmc<=(-1),
            "galtan.z.gmc"])


p$filter.low<-
  ifelse(p$galtan_salience.z.gmc==(-1) &
           (p$galtan.z.gmc<min.low | 
              p$galtan.z.gmc>max.low),0,1)

table(p$filter.low)

min.mid<-
  min(exdat[exdat$galtan_salience.z.gmc>(-1) |
              exdat$galtan_salience.z.gmc<(1),
            "galtan.z.gmc"])
max.mid<-
  max(exdat[exdat$galtan_salience.z.gmc>(-1) |
              exdat$galtan_salience.z.gmc<(1),
            "galtan.z.gmc"])


p$filter.mid<-
  ifelse(p$galtan_salience.z.gmc==(0) &
           (p$galtan.z.gmc<min.mid | 
              p$galtan.z.gmc>max.mid),0,1)

table(p$filter.mid)

min.high<-
  min(exdat[exdat$galtan_salience.z.gmc>=(1) ,
            "galtan.z.gmc"])
max.high<-
  max(exdat[exdat$galtan_salience.z.gmc>=(1) ,
            "galtan.z.gmc"])



p$filter.high<-
  ifelse(p$galtan_salience.z.gmc==(1) &
           (p$galtan.z.gmc<min.high | 
              p$galtan.z.gmc>max.high),0,1)

table(p$filter.high)

p.ex<-p[p$filter.low!=0 & p$filter.mid!=0 & p$filter.high!=0,]


p1<-ggplot(p.ex,aes(y=yvar,x=xvar,color=galtan_salience))+
  geom_point()+
  geom_errorbar(aes(ymin=LCL, ymax=UCL),alpha=0.5)+
  xlab("Left-Right Economic")+
  ylab("P(Childlessness)")
p1

png(filename = 
      "../../results/figures/galtan_galtan_salience_nonextrp.png",
    units = "cm",
    width = 20.0,height=10.0,res = 300)
p1
dev.off()
```

### marginal effects

```{r}
emtrends(mod6.galtan,
         var="galtan.z.gmc",
         specs="galtan_salience.z.gmc",
         at=list(galtan_salience.z.gmc=c(-1,0,1)),infer=c(T,T))
```

# ERQ1 Analysis 

ERQ1. If childlessness is associated with the economic left-right position of the party for which one has voted, are those associations stronger if this dimension is salient in the party’s public stance (i.e., is there a boundary condition to these associations, such that the ideology needs to be salient in order for the association to exist)?


## lrecon salience fixed main effect

```{r}
mod4.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+lrecon_salience.z.gmc+
          (lrecon.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod4.lrecon)
```

## fixed interaction between lrecon and lrecon salience

```{r}
mod5.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+lrecon_salience.z.gmc+
          lrecon.z.gmc:lrecon_salience.z.gmc+
          (lrecon.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod5.lrecon)
```

### marginal effects

```{r}
emtrends(mod5.lrecon,
         var="lrecon.z.gmc",
         specs="lrecon_salience.z.gmc",
         at=list(lrecon_salience.z.gmc=c(-1,0,1)),infer=c(T,T))
```



## random interaction between lrecon and lrecon salience

```{r}
mod6.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+lrecon_salience.z.gmc+
          lrecon.z.gmc:lrecon_salience.z.gmc+
          (lrecon.z.gmc+lrecon_salience.z.gmc+
             lrecon.z.gmc:lrecon_salience.z.gmc||cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod6.lrecon)
```

### marginal effects

```{r}
emtrends(mod6.lrecon,
         var="lrecon.z.gmc",
         specs="lrecon_salience.z.gmc",
         at=list(lrecon_salience.z.gmc=c(-1,0,1)),infer=c(T,T))
```

## exclude all random slopes

```{r}
mod7.lrecon<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          lrecon.z.gmc+lrecon_salience.z.gmc+
          lrecon.z.gmc:lrecon_salience.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa",
                               optCtrl=list(maxfun=2e6)))
summary(mod7.lrecon)
anova(mod7.lrecon,mod6.lrecon)
```

### Plot

```{r}

p<-
  emmip(mod7.lrecon, lrecon_salience.z.gmc ~ lrecon.z.gmc,
        at=list(lrecon_salience.z.gmc = c(-1,0,1),
                #minority.c = c(-0.5,0.5),
                lrecon.z.gmc=seq(from=-2,to=2,by=0.02)),
        plotit=F,CIs=TRUE,type="response")

head(p)

#p$ethnic_minority=
#  ifelse(p$minority.c==(-0.5),
#         "Ethnic majority","Ethnic minority")
p$lrecon_salience<-p$tvar
levels(p$lrecon_salience)



p2<-ggplot(p,aes(y=yvar,x=xvar,color=lrecon_salience))+
  geom_point()+
  geom_errorbar(aes(ymin=LCL, ymax=UCL),alpha=0.5)+
  xlab("Left-Right Economic")+
  ylab("P(Childlessness)")
p2

png(filename = 
      "../../results/figures/lrecon_lrecon_salience.png",
    units = "cm",
    width = 20.0,height=10.0,res = 300)
p2
dev.off()
```

### Non-extrapolated plot

```{r}
quantile(exdat$lrecon_salience.z.gmc,
         seq(0,1,0.10))

prop.table(table(exdat$lrecon_salience.z.gmc>1))
prop.table(table(exdat$galtan_salience.z.gmc>1))

min.low<-
  min(exdat[exdat$lrecon_salience.z.gmc<=(-0.8),
            "lrecon.z.gmc"])
max.low<-
  max(exdat[exdat$lrecon_salience.z.gmc<=(-0.8),
            "lrecon.z.gmc"])


p$filter.low<-
  ifelse(p$lrecon_salience.z.gmc==(-1) &
           (p$lrecon.z.gmc<min.low | 
              p$lrecon.z.gmc>max.low),0,1)

table(p$filter.low)

min.mid<-
  min(exdat[exdat$lrecon_salience.z.gmc>(-0.8) |
              exdat$lrecon_salience.z.gmc<(0.8),
            "lrecon.z.gmc"])
max.mid<-
  max(exdat[exdat$lrecon_salience.z.gmc>(-0.8) |
              exdat$lrecon_salience.z.gmc<(0.8),
            "lrecon.z.gmc"])


p$filter.mid<-
  ifelse(p$lrecon_salience.z.gmc==(0) &
           (p$lrecon.z.gmc<min.mid | 
              p$lrecon.z.gmc>max.mid),0,1)

table(p$filter.mid)

min.high<-
  min(exdat[exdat$lrecon_salience.z.gmc>=(0.8) ,
            "lrecon.z.gmc"])
max.high<-
  max(exdat[exdat$lrecon_salience.z.gmc>=(0.8) ,
            "lrecon.z.gmc"])


p$filter.high<-
  ifelse(p$lrecon_salience.z.gmc==(1) &
           (p$lrecon.z.gmc<min.high | 
              p$lrecon.z.gmc>max.high),0,1)

table(p$filter.high)

p.ex<-p[p$filter.low!=0 & p$filter.mid!=0 & p$filter.high!=0,]


p1<-ggplot(p.ex,aes(y=yvar,x=xvar,color=lrecon_salience))+
  geom_point()+
  geom_errorbar(aes(ymin=LCL, ymax=UCL),alpha=0.5)+
  xlab("Left-Right Economic")+
  ylab("P(Childlessness)")
p1

png(filename = 
      "../../results/figures/lrecon_lrecon_salience_nonextrp.png",
    units = "cm",
    width = 20.0,height=10.0,res = 300)
p1
dev.off()
```

# ERQ2 Analysis

## Data exclusions

```{r}
PP.vars<-
  names(fdat)[which(names(fdat)=="spendvtax.z"):
                which(names(fdat)=="corrupt_salience.z")]

exdat<-fdat %>%
  dplyr::select(childlessness,
                gndr.c,age10.c,
                minority.c,all_of(PP.vars),
                cntry,anweight) %>%
  na.omit()
```

## Variable centering

```{r}
exdat<-
  group_mean_center(data=exdat,
                    group.var="cntry",
                    vars=PP.vars,
                    grand.init = F)
names(exdat)
```

## spendvtax

### Fixed

```{r}

mod2.spendvtax<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          spendvtax.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.spendvtax)
```

### Random

```{r}
mod3.spendvtax<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          spendvtax.z.gmc+
          (spendvtax.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.spendvtax)

anova(mod2.spendvtax,mod3.spendvtax)
```

## deregulation

### Fixed

```{r}

mod2.deregulation<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          deregulation.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.deregulation)
```

### Random

```{r}
mod3.deregulation<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          deregulation.z.gmc+
          (deregulation.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.deregulation)

anova(mod2.deregulation,mod3.deregulation)
```

## redistribution

### Fixed

```{r}

mod2.redistribution<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          redistribution.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.redistribution)
```

### Random

```{r}
mod3.redistribution<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          redistribution.z.gmc+
          (redistribution.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.redistribution)

anova(mod2.redistribution,mod3.redistribution)
```

## econ_interven

### Fixed

```{r}

mod2.econ_interven<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          econ_interven.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.econ_interven)
```

### Random

```{r}
mod3.econ_interven<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          econ_interven.z.gmc+
          (econ_interven.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.econ_interven)

anova(mod2.econ_interven,mod3.econ_interven)
```



## civlib_laworder

### Fixed

```{r}

mod2.civlib_laworder<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          civlib_laworder.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.civlib_laworder)
```

### Random

```{r}
mod3.civlib_laworder<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          civlib_laworder.z.gmc+
          (civlib_laworder.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.civlib_laworder)

anova(mod2.civlib_laworder,mod3.civlib_laworder)
```

## sociallifestyle

### Fixed

```{r}

mod2.sociallifestyle<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          sociallifestyle.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.sociallifestyle)
```

### Random

```{r}
mod3.sociallifestyle<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          sociallifestyle.z.gmc+
          (sociallifestyle.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.sociallifestyle)

anova(mod2.sociallifestyle,mod3.sociallifestyle)
```

## religious_principle

### Fixed

```{r}

mod2.religious_principle<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          religious_principle.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.religious_principle)
```

### Random

```{r}
mod3.religious_principle<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          religious_principle.z.gmc+
          (religious_principle.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.religious_principle)

anova(mod2.religious_principle,mod3.religious_principle)
```

## immigrate_policy

### Fixed

```{r}

mod2.immigrate_policy<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          immigrate_policy.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.immigrate_policy)
```

### Random

```{r}
mod3.immigrate_policy<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          immigrate_policy.z.gmc+
          (immigrate_policy.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.immigrate_policy)

anova(mod2.immigrate_policy,mod3.immigrate_policy)
```

## multiculturalism

### Fixed

```{r}

mod2.multiculturalism<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          multiculturalism.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.multiculturalism)
```

### Random

```{r}
mod3.multiculturalism<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          multiculturalism.z.gmc+
          (multiculturalism.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.multiculturalism)

anova(mod2.multiculturalism,mod3.multiculturalism)
```

## urban_rural

### Fixed

```{r}

mod2.urban_rural<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          urban_rural.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.urban_rural)
```

### Random

```{r}
mod3.urban_rural<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          urban_rural.z.gmc+
          (urban_rural.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.urban_rural)

anova(mod2.urban_rural,mod3.urban_rural)
```

## environment

### Fixed

```{r}

mod2.environment<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          environment.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.environment)
```

### Random

```{r}
mod3.environment<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          environment.z.gmc+
          (environment.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.environment)

anova(mod2.environment,mod3.environment)
```

## regions

### Fixed

```{r}

mod2.regions<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          regions.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.regions)
```

### Random

```{r}
mod3.regions<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          regions.z.gmc+
          (regions.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.regions)

anova(mod2.regions,mod3.regions)
```

## international_security

### Fixed

```{r}

mod2.international_security<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          international_security.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.international_security)
```

### Random

```{r}
mod3.international_security<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          international_security.z.gmc+
          (international_security.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.international_security)

anova(mod2.international_security,mod3.international_security)
```

## ethnic_minorities

### Fixed

```{r}

mod2.ethnic_minorities<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          ethnic_minorities.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.ethnic_minorities)
```

### Random

```{r}
mod3.ethnic_minorities<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          ethnic_minorities.z.gmc+
          (ethnic_minorities.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.ethnic_minorities)

anova(mod2.ethnic_minorities,mod3.ethnic_minorities)
```

## nationalism

### Fixed

```{r}

mod2.nationalism<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          nationalism.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.nationalism)
```

### Random

```{r}
mod3.nationalism<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          nationalism.z.gmc+
          (nationalism.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.nationalism)

anova(mod2.nationalism,mod3.nationalism)
```
## antielite_salience

### Fixed

```{r}

mod2.antielite_salience<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          antielite_salience.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.antielite_salience)
```

### Random

```{r}
mod3.antielite_salience<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          antielite_salience.z.gmc+
          (antielite_salience.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.antielite_salience)

anova(mod2.antielite_salience,mod3.antielite_salience)
```



## corrupt_salience

### Fixed

```{r}

mod2.corrupt_salience<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          corrupt_salience.z.gmc+
          (1|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight)
summary(mod2.corrupt_salience)
```

### Random

```{r}
mod3.corrupt_salience<-
  glmer(childlessness~gndr.c+age10.c+minority.c+
          corrupt_salience.z.gmc+
          (corrupt_salience.z.gmc|cntry),
        data=exdat,
        family=binomial(link="logit"),weights = anweight,
        control = glmerControl(optimizer="bobyqa"))
summary(mod3.corrupt_salience)

anova(mod2.corrupt_salience,mod3.corrupt_salience)
```

```{r}
sinf<-sessionInfo()
print(sinf,locale=F)
```
